A pipeline to analyse time-course gene expression data

### 2019-05-15 scripts/manuscript.Rmd
Update the manuscript to use the helper function

variance_filtered_data = variance_filtered_data[, ord]
data_corr = stats::cor(variance_filtered_data, method="pearson")

data_corr_meta = meta[ord, ]

# Copy the metadata before changing the timepoints into factors
data_corr_meta$Timepoint = as.factor(meta$Timepoint)
NMF::aheatmap(
    data_corr,
    Colv=NA, Rowv=NA,
    annCol=data_corr_meta[, c("Group", "Timepoint")],
    annRow=data_corr_meta[, c("Group", "Timepoint")],
    annLegend=TRUE, 
    annColors=ann_colors,
    main="Correlation plot")
```

@@

Here, we show an example where we define our contrasts to be the difference
between the control mouse ("M") and the mouse infected with the high dose of
the influenza strain A/Vietnam/1203/04 (H5N1) ("VL") for each time point, but
the function works with any form contrasts. **FIXME: Reference to limma
vignette for how to define the contrasts** **EAP: Could you make simple
function that creates them automatically for two conditions -- i.e. find union
of time points for two conditions... Then we could show an example with just a
couple done manually, and then say we can also use a little helper function in
the `moanin` that will do it for all time points**

**Add a helper function to make the contrasts for timely DE**

```{r weekly_differential_analysis}
meta$WeeklyGroup = make.names(meta$Group:as.factor(meta$Timepoint))

# Define contrast	
contrasts = c("M.0-VL.0",
	      "M.3-VL.3",
	      "M.6-VL.6",
	      "M.9-VL.9",
	      "M.12-VL.12",
	      "M.18-VL.18",
	      "M.24-VL.24",
	      "M.30-VL.30",
	      "M.36-VL.36",
	      "M.48-VL.48",
	      "M.60-VL.60",
	      "M.72-VL.72",
	      "M.120-VL.120",
	      "M.168-VL.168")
weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)
```

@@

```{r echo=FALSE, results="hide"}
# Hide those results
# Run the DE analysis on the rest of the influenza strain.
contrasts = c("M.0-K.0",
	      "M.3-K.3",
	      "M.6-K.6",
	      "M.9-K.9",
	      "M.12-K.12",
	      "M.18-K.18",
	      "M.24-K.24",
	      "M.30-K.30",
	      "M.36-K.36",
	      "M.48-K.48",
	      "M.60-K.60",
	      "M.72-K.72",
	      "M.120-K.120",
	      "M.168-K.168")
K_weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-C.0",
	      "M.3-C.3",
	      "M.6-C.6",
	      "M.9-C.9",
	      "M.12-C.12",
	      "M.18-C.18",
	      "M.24-C.24",
	      "M.30-C.30",
	      "M.36-K.36",
	      "M.48-C.48",
	      "M.60-C.60",
	      "M.72-C.72",
	      "M.120-C.120",
	      "M.168-C.168")
C_weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)
contrasts = c("M.0-VH.0",
	      "M.3-VH.3",
	      "M.6-VH.6",
	      "M.9-VH.9",
	      "M.12-VH.12",
	      "M.18-VH.18",
	      "M.24-VH.24",
	      "M.30-VH.30",
	      "M.36-VH.36",
	      "M.48-VH.48",
	      "M.60-VH.60",
	      "M.72-VH.72",
	      "M.120-VH.120",
	      "M.168-VH.168")
VH_weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)

>>>>

variance_filtered_data = variance_filtered_data[, ord]
data_corr = stats::cor(variance_filtered_data, method="pearson")
data_corr_meta = meta[ord, ]
data_corr_meta$Timepoint = as.factor(data_corr_meta$Timepoint)

NMF::aheatmap(
    data_corr,
    Colv=NA, Rowv=NA,
    annCol=data_corr_meta[, c("Group", "Timepoint")],
    annRow=data_corr_meta[, c("Group", "Timepoint")],
    annLegend=TRUE, 
    annColors=ann_colors,
    main="Correlation plot")
```

@@

Here, we show an example where we define our contrasts to be the difference
between the control mouse ("M") and the mouse infected with the high dose of
the influenza strain A/Vietnam/1203/04 (H5N1) ("VL") for each time point, but
the function works with any form contrasts [@ritchie:limma].

First, create the contrasts for all timepoints between the two groups of
interest:
```{r make_timepoints_contarts}
contrasts = create_timepoints_contrasts("M", "VL", splines_model)
```

```{r echo=FALSE}
kable(contrasts)
```

Then run the differential expression analysis on all of those timepoints
jointly.

```{r weekly_differential_analysis}
# Define contrast	
weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)
```

```{r echo=FALSE}
kable(weekly_de_analysis[1:10, ])
```

@@

```{r echo=FALSE, results="hide"}
contrasts = create_timepoints_contrasts("M", "K", splines_model)
K_weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)

contrasts = create_timepoints_contrasts("M", "C", splines_model)
C_weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)

contrasts = create_timepoints_contrasts("M", "VH", splines_model)
VH_weekly_de_analysis =  moanin::DE_timepoints(
     data, splines_model, contrasts,
     use_voom_weights=FALSE)
